Network Configuration Synthesis with Abstract Topologies

### 2016-11-11 paper/abstraction/appendix.tex
update proof

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m = (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(\{b\in f^{-1}(B), (b,\ell) \in G.E, B \in BS\},q_N) ~\vert~ (\_,q_N) \in I, BS=\{B~\vert~ (B,q_N) \in I \} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \text{adjOut}(PG^A,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m = (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ I = \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in I\} \}) \\
     ~~~~~~~~~~~~~~~~~~ out = \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG,m) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  \begin{proof}
    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$. Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism. For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism. Thus by taking $\bigcup f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph. However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph. This is because we know $q_n \rightarrow q_m$ from the abstract product graph is a valid transition and the topology edge exists.
  \end{proof}

\ryan{Update me}

@@

\vspace{2em}
\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:

@@

  \vspace{1em}
  \begin{proof} \text{ }

@@

  \[ \begin{array}{l}
     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_j = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \} \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M = (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin = \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) = \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \} \\
     ~~~~~~~~~~~~~~~~~~ out = con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)) \\
     ~~~~~~~~~~~~~~~~~~ ma_{q_N} = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

>>>>

  \end{minipage}
  %
  %
  \begin{minipage}[t]{.5\linewidth}
  \hdr{Compilation}{}
  \vspace*{-1\baselineskip}
  %
  \[ \begin{array}{l}
     \text{compile}_\text{ABGP}( (t_1,PG_1,ord_1), \dots, (t_k,PG_k,ord_k), G ) = \\
     ~~~~~ [~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_m) \in PG_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG_i,m), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (bs,q_n) ~\vert~ (\_,q_n) \in pin, bs=\{b ~\vert~ (b,q_n) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \text{adjOut}(PG_i,m) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord_i(m) : (in,q_n) \rightarrow (out,q_m) ~] ~] \\
     \\
     \text{compile}( p_1, \dots, p_k, G) = \\
     ~~~~~~ \text{compile}_\text{ABGP}(\text{compile}_\text{PG}(p_1,G), \dots, \text{compile}_\text{PG}(p_k,G), G) \\
  \end{array} \]%
  \end{minipage}%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A, \\
     ~~~~~~~~~~~~~~~~~~ pin = \mathit{adjIn}(PG^A,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \in \{(BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in pin \} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ c \in f^{-1}(C), (c,\ell) \in G.E, (C,\_) \in \mathit{adjOut}(PG^A,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ pfx \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ m \leftarrow (l,q_M) \in PG, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG,m), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in I, bs=\{ b ~\vert~ (b,q_N) \in pin\} \}), \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ c ~\vert~ (c,\_) \in \mathit{adjOut}(PG,m) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A(f_{pg}(m)) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

  \begin{proof}
    For each $M$ there exists at least one $m$ such that $f_{pg}(m) = M$. Note that $f_{pg}$ overapproximates the connectivity of the product graph, by virtue of being a graph homomorphism. For each concrete node $n$ such that $n = (b,q_n) \in adjIn(PG,m)$ we know that if $f_{pg}(n) = N$ where $N = (f(b),q_N)$, then $N \in adjIn(PG^A,M)$ and $q_n = q_N$ from the homomorphism. Thus by taking $f^{-1}(B) = f^{-1}(f(b))$, for each such $f(b)$ for node $N$ that shares the same state $q_N$, we get a superset of the locations from the concrete graph. However, by restricting those locations to only those that appear in the topology $(b,\ell)$, we get exactly the set that appears in the concrete product graph. 
    This is because we know $q_N \rightarrow q_M$ from the abstract product graph is a valid transition, which means that $q_n \rightarrow q_m$ is a valid concrete product graph transition, and if there is a topology edge $(b,\ell)$, then there must be a product graph edge $(n,m)$. Therefore:
    $$\{b ~\vert~ b \in f^{-1}(B),~ (b,\ell) \in G.E,~ (B,q_N) \in \text{adjIn}(PG^A,f_{pg}(m)) \}$$
    is equivalent to
    $$\{ b ~\vert~ (b,q_N) \in \text{adjIn}(PG,m)\}$$
    This also holds for the case with adjOut. Further, note that because we are looking at a particular location $l$, there can only be at most one such $m = (l,q_N)$ such that $f_{pg}(m) = M = (f(l), q_N)$. If there is no such $m$ where $f_{pg}(m) = M$, then the above expression will produce the empty set after filtering with the topology. Going over each $M$ then is equivalent to going over each $m$ so long as we throw away imports $\mathit{in}$ that are empty.

@@

\begin{thm}
  For any context $\Gamma$, concrete topology $G$, abstract topology $G^A$, homomorphism $f : G \rightarrow G^A$:

@@

  \begin{proof} \text{ }

@@

  \[ \begin{array}{l}
     ~~~~~ con([~ l \rightarrow rc ~\vert~ \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_n) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~], \Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (bs,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_n) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = con(\mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ [~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~ [~ \ell \rightarrow con(rc,\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~ \ell \in f^{-1}(l), \\
     ~~~~~~~~~ l \in internal(G^A.V), \\
     ~~~~~~~~~ rc = \mathit{append}_i~  \\
     ~~~~~~~~~~~~~~~ con([~ t_i \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(m) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ con([~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~],\ell,\Gamma,f,G) \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1, \dots, ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow con(ma_1,\text{true},\ell,\Gamma,f,G), \dots, con(ma_k,\text{true},\ell,\Gamma,f,G) ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = con(ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\text{true},\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (in,q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow \{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \}, \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (con(in,\ell,\Gamma,f,G),q_N) \rightarrow (con(out,\ell,\Gamma,f,G),q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%

@@

  \[ \begin{array}{l}
     ~~~~~~~~~ [~ \Pfx_{i1} \rightarrow ma_1, \dots, ma_k ~\vert~ \\
     ~~~~~~~~~~~~~~~~~~ M \leftarrow (l,q_M) \in PG^A_i, \\
     ~~~~~~~~~~~~~~~~~~ pin \leftarrow \text{adjIn}(PG^A_i,M), \\
     ~~~~~~~~~~~~~~~~~~ (con(in,\ell,\Gamma,f,G),q_N) \leftarrow \{ (BS,q_N) ~\vert~ (\_,q_N) \in pin, BS=\{B ~\vert~ (B,q_N) \in pin \} \}, \\
     ~~~~~~~~~~~~~~~~~~ out \leftarrow con(\{ C ~\vert~ (C,\_) \in \text{adjOut}(PG^A_i,M) \},\ell,\Gamma,f,G)), \\
     ~~~~~~~~~~~~~~~~~~ in \neq \emptyset, \\
     ~~~~~~~~~~~~~~~~~~ ma_h = ord^A_i(M) : (in,q_N) \rightarrow (out,q_M),\ell,\Gamma,f,G) ~] \\
  \end{array} \]%
